Plot curve fits

### 2023-01-12 Working Rmds/plot_fits.Rmd
Rename "Routes" and "Media" to "N_Routes" and "N_Media" to avoid collision with column names of CVT data (which contain a "Media" column that is really singular "Medium")

```{r}
timestamp <- "2023_01_06"
```

@@

```{r, load_cvt, eval = TRUE}
cvt <- fread("../inst/ext/cvt_preprocessed_2023_01_06.csv")
cvt[, Reference:=as.character(Reference)]
cvt[, Reference_orig:=as.character(Reference_orig)]
```

@@

PK.fit.table.1comp <- fread(paste0("../inst/ext/", "PK_fit_table_1comp_", timestamp, ".csv",sep=""))
PK.fit.table.2comp <- fread(paste0("../inst/ext/", "PK_fit_table_2comp_", timestamp, ".csv",sep=""))
PK.fit.table.flat <- fread(paste0("../inst/ext/", "PK_fit_table_flat_", timestamp, ".csv",sep=""))

@@

Rowbind together all of the fitted parameter tables into one big one.
```{r}
pk_fit <- rbindlist(list("1comp" = PK.fit.table.1comp,
                         "2comp" = PK.fit.table.2comp,
                         "flat" = PK.fit.table.flat),
                    use.names = TRUE,
                    fill = TRUE)

rm(PK.fit.table.1comp,
   PK.fit.table.2comp,
   PK.fit.table.flat)
```

Get a table of the winning model for each dataset (the one with minimum AIC).

```{r}
tmp <- unique(pk_fit[, .(DTXSID, Species, Analysis_Type, References.Analyzed, model, AIC)])

#sort AIC from smallest to largest within each dataset, putting NAs last
setorder(tmp, DTXSID, Species, Analysis_Type, References.Analyzed, AIC, na.last = TRUE)
#the winning model will now be listed first within each dataset (smallest AIC)
model_win <- tmp[, .(winmodel = model[1]), by = .(DTXSID, Species, Analysis_Type, References.Analyzed)]
pk_fit <- model_win[pk_fit, on = c("DTXSID", "Species", "Analysis_Type", "References.Analyzed")]
pk_fit[, winning:=(model == winmodel)]

@@

Plot all models for the joint analysis.
```{r}

#plot all models
tmp <- mapply(plot_fit,
              DTXSID_in = plot_table$DTXSID,
                     Species_in = plot_table$Species,
              MoreArgs = list(
                     model_in = "all",
                     Analysis_Type_in = "Joint",
                     DF = cvt,
                     pk_fit = pk_fit,
                     n_interp_time = 10,
                     limit_y_axis = FALSE,
                     log10_scale_y = FALSE,
                     plot_errbars = TRUE,
                     log10_scale_time = FALSE,
                     file_path = "../inst/ext/plots/Joint Analysis/model_all/errbars_naturaly")
                     )

>>>>

```{r}
timestamp <- "2023_01_11"
```

@@

```{r, load_cvt, eval = TRUE}
cvt <- fread(paste0("../inst/ext/cvt_preprocessed_",
timestamp,
".csv"))
cvt[, Reference:=as.character(Reference)]
cvt[, Reference_orig:=as.character(Reference_orig)]
```

@@

DT_1comp <- fread(paste0("../inst/ext/", "PK_fit_postprocess_1comp_", timestamp, ".csv",sep=""))
DT_2comp <- fread(paste0("../inst/ext/", "PK_fit_postprocess_2comp_", timestamp, ".csv",sep=""))
DT_flat <- fread(paste0("../inst/ext/", "PK_fit_postprocess_flat_", timestamp, ".csv",sep=""))

idcols <- c( "Analysis_Type",
                                 "DTXSID",
                                "Species",
                                "References.Analyzed",
                               "Studies.Analyzed",
                               "N_Routes",
                               "N_Media",
              "time_units_reported")

setnames(DT_1comp,
         setdiff(names(DT_1comp),
                 idcols),
         paste(setdiff(names(DT_1comp),
                 idcols),
               "1compartment",
               sep = "."))

setnames(DT_2comp,
         setdiff(names(DT_2comp),
                 idcols),
         paste(setdiff(names(DT_2comp),
                 idcols),
               "2compartment",
               sep = "."))

setnames(DT_flat,
         setdiff(names(DT_flat),
                 idcols),
         paste(setdiff(names(DT_flat),
                 idcols),
               "flat",
               sep = "."))

@@

Merge these together.

```{r}
pk_fit <- merge(DT_2comp,
               merge(DT_flat, DT_1comp, by = idcols),
               by = idcols)
```

Find the winning model for each dataset

```{r}
pk_AIC <- melt(pk_fit,
     id.vars = idcols,
     measure.vars = c("AIC.flat",
                      "AIC.1compartment",
                      "AIC.2compartment"),
     value.name = "AIC",
     variable.name = "model")

pk_AIC[, model := gsub(x = model,
                       pattern = "AIC.",
                       replacement = "",
                       fixed = TRUE)]

#sort AIC from smallest to largest within each dataset, putting NAs last
setorderv(pk_AIC,
        c(idcols, "AIC"),
         na.last = TRUE)
#the winning model will now be listed first within each dataset (smallest AIC)
model_win <- pk_AIC[,
                    .(winmodel = model[1]),
                    by = idcols]
pk_fit <- model_win[pk_fit,
                    on = idcols]
```

Keep parameters only.

```{r}
all_params <- unlist(sapply(c("flat",
         "1compartment",
         "2compartment"),
       function(model){
         tmp <- get_model_paramnames(model)
         return(paste(tmp,
                      model,
                      sep= "."))
       }))

pk_params <- pk_fit[, .SD, .SDcols = c(idcols, "winmodel", all_params)]

#Ensure comma-separated lists of studies analyzed are properly sorted
pk_params[, Studies.Analyzed := {
  tmp <- strsplit(x = Studies.Analyzed,
           split = ", ")
  sapply(tmp,
         function(x) paste(sort(x), collapse = ", "))
}]

# pk_params[is.na(Fgutabs_Vdist.flat),
#           Fgutabs_Vdist.flat := Fgutabs.flat / Vdist.flat]
# 
# pk_params[is.na(Rblood2plasma.flat), Rblood2plasma.flat := 1]
# pk_params[is.na(Rblood2plasma.1compartment), Rblood2plasma.1compartment := 1]
# pk_params[is.na(Rblood2plasma.2compartment), Rblood2plasma.2compartment := 1]
```

Merge the parameter information with the original concentration-time info.

```{r}
cvt[, Study_pooled :=
  paste(
    sort(unique(Study)),
    collapse = ", "
  ),
  by = .(DTXSID, Species)]

  #Melt to longer format. The effect will be as though we row-bound two versions
  #of DF together: one with the original single references, and one with
  #comma-separated combined References. There is one column "Study_type" that
  #contains either "Study" or "Study_pooled", and then one column "Study" that
  #contains the studyID or the comma-separated list of study IDs.
  cvt1 <- melt(cvt,
              measure.vars = c("Study", "Study_pooled"),
              variable.name = "Study_type",
              value.name = "Study")

  #There will be duplicated rows for single-study analyses, because
  #"Study_pooled" (the comma-separated list of study IDs) is the same as "Study"
  #(the individual study ID) for these analyses. Remove the duplicated rows.
  cvt1 <- unique(cvt1[, .(DTXSID, Compound, Species, Study,Reference,
                        Route, Dose, iv, Media, Time, Value, LOQ, Value_SD, N_Subjects)])

  cvt_fit <- pk_params[cvt1, 
                    on = c("DTXSID" = "DTXSID",
                            "Species" = "Species",
                            "Studies.Analyzed" = "Study"),
                     allow.cartesian = TRUE]
```

@@

Plot all models for the joint analysis.
```{r}
cvt_fit[,
        plot_fit(DTXSID = unique(DTXSID),
                 Species_in = unique(Species),
                 DFsub = .SD,
                 model_in = "all",
                 Analysis_Type_in = "Joint",
                 n_interp_time = 10,
                     limit_y_axis = FALSE,
                     log10_scale_y = FALSE,
                     plot_errbars = TRUE,
                     log10_scale_time = FALSE,
                     file_path = "../inst/ext/plots/Joint Analysis/model_all/errbars_naturaly",
                 verbose = TRUE),
        by = .(DTXSID,
               Species),
        .SDcols = names(cvt_fit)]
